--- 
title: "Online Notes for ACTS 131"
author: "John Garza"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is an experiment for using bookdown to generate course notes"
---







<!--chapter:end:index.Rmd-->

# Introduction 



```{r nice-fig, fig.cap='Using ggplot2', out.width='80%',fig.align = 'center', message = FALSE, warning = FALSE}
library(dplyr)
library(ggplot2)
mtcars$cyl <- as.factor(mtcars$cyl)
mtcars %>%
  ggplot(aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point() +
  facet_wrap(~am)
```

```{r}
curve(dnorm(x, mean = 0, sd = 1), col = 'blue', lwd =2)
```



```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```


<!--chapter:end:01-Introduction.Rmd-->

# Probability

<!--chapter:end:02-probability.Rmd-->

# Discrete Distributions


<!--chapter:end:03-discrete.Rmd-->

# Continuous Distributions

<!--chapter:end:04-continuous.Rmd-->

# Multivariable Distributions

<!--chapter:end:05-multivariable.Rmd-->

# Functions of a Random Variable

<!--chapter:end:06-functions.Rmd-->

# The Central Limit Theorem

<!--chapter:end:07-central.Rmd-->

---
title: "show1"
author: "John Garza"
date: "February 7, 2017"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
library(ggvis)
```

```{r echo = TRUE, message = FALSE}
slider <- input_slider(10, 1000)
mtcars %>% ggvis(~wt, ~mpg) %>%
  layer_points(fill := "red", size := slider) %>%
  layer_points(stroke := "black", fill := NA, size := slider)
```

<!--chapter:end:show1.Rmd-->

---
title: "Untitled"
author: "John Garza"
date: "February 7, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```


<!--chapter:end:tre.Rmd-->

